Excuse me, do you have a moment to talk about version control?

### 2017-10-05 README.Rmd
Convert a set of bullet points to a paragraph

If I've convinced you to experiment with Git and GitHub, you need to do some initial setup. These first steps happen once or, for some steps, once per computer. This is excerpted from [Happy Git and GitHub for the useR](http://happygitwithr.com), which holds battle-tested instructions honed over several years in [STAT 545](http://stat545.com) at the University of British Columbia.

@@

Once this setup is done, you are ready to start using Git and GitHub with your 
projects. Some general recommendations for agony reduction:

  * I repeat: consider using a graphical front-end for Git, a.k.a. a Git client, versus restricting yourself to the command line interface.
  * Establish confidence in the basics (e.g. make a change, commit it, push it) before wading into more advanced usage (e.g. branching).
  * Commit yourself to Git usage on a project that will provide sustained practice over several months. Usage in a course is great, because it provides a relentless stream of small deadlines.
  * Realize that no one is giving out Git style points. It's OK to "power-cycle", i.e. re-initialize the Git repository, to get unstuck.

>>>>

If I've convinced you to experiment with Git and GitHub, you need to do some initial setup. These first steps happen once or, for some steps, once per computer. These instructions are excerpted from [Happy Git and GitHub for the useR](http://happygitwithr.com), which holds battle-tested instructions honed over several years in [STAT 545](http://stat545.com) at the University of British Columbia.

@@

Once this setup is done, you are ready to start using Git and GitHub with your 
projects. Here are some general recommendations for agony reduction. As suggested above, it may be worth using a graphical front-end for Git, a.k.a. a Git client, versus restricting yourself to the command line interface. It is fruitful to establish confidence in basic operations (e.g. make a change, commit it, push it) before wading into more advanced usage (e.g. branching). It is helpful to begin with a project that will provide sustained practice over several months. For example, usage in a course is great, because it provides a relentless stream of small deadlines. Finally, it is liberating to realize that no one is giving out Git style points. It is acceptable to "power-cycle", i.e. re-initialize the Git repository, to get unstuck.
